---
title: "Evocative Videos Results and Figures"
author: "Jake Portanova"
date: "October 31, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(xlsx)
library(wordspace)
library(ROCR)
setwd("C:/Users/jakep/Desktop")
demo <- read.csv("PORQ_demographicAndBaselineDayData_labeled_scales.csv")

setwd("C:/Users/jakep/Dropbox/PORQ_dataForUW/evocativeVideoTask")
evoc_trans <- read.xlsx("PORQ_evocativeVideoTask_transcripts.xlsx", sheetIndex = 1)

# read unbinding
setwd("..")
unblinding <- read.xlsx("PORQ_drugUnblinding.xlsx", sheetIndex = 1)

# IDDay
evoc_trans$IDDay <- paste(evoc_trans$participantID, evoc_trans$day, sep="_")
unblinding$IDDay <- paste(unblinding$participantID, unblinding$day, sep="_")

# Join on ID Day
data <- full_join(unblinding, evoc_trans, by="IDDay")
data[is.na(data$drugCondition),c("drugCondition")] <- "PL"
# filter for only placebo
data <- data %>% filter(drugCondition == "PL")
data$file <- paste(data$participantID.y,data$stimulus,sep="_")
setwd("C:/Users/jakep/Desktop")
coherence <- read.csv("coherenceresult.csv")
coherencepl <- left_join(coherence, data, by="file")
coherencepl$id <- substr(coherencepl$file,1,4)
coherenceplr <- coherencepl %>% group_by(id) %>% summarise_all(funs(mean(., na.rm = TRUE)))
cohdemo <- inner_join(coherenceplr,demo,by="id")
cohdemo$LackOfSpontaneityFlowOfConverstation <- cohdemo$X8..Lack.of.Spontaneity.Flow.of.Conversation   
cohdemo$ConceptualDisorganization <- cohdemo$X13..Conceptual.Disorganization
cohdemo$IncoherentSpeech <- cohdemo$X14..Incoherent.Speech                                        
cohdemo$PovertyOfSpeechContent <- cohdemo$X15..Poverty.of.Speech.Content 

## T-test and ROC GoEmo Processing
setwd("C:/Users/jakep/Desktop")
goemo <- read.csv("go_emotions_output.csv")
goemo$Filename <- substr(goemo$file, 17,50) # get filename
goemo$id <- sapply(strsplit(goemo$Filename, "_"), "[", 1)
goemo$emo <- sapply(strsplit(goemo$Filename, "_"), "[", 2)
goemo$thing <- sapply(strsplit(goemo$Filename, "_"), "[", 3)
goemo <- goemo[-which(goemo$thing=="heart"),]
goemo$feeldescribe <- sapply(strsplit(goemo$Filename, "_"), "[", 4)
goemo <- goemo[grep("feel",goemo$feeldescribe),]
goemo$Filename <- paste(goemo$id,goemo$emo,goemo$thing, sep="_")
# Create variable for joining
data$Filename <- paste(data$participantID.y,data$stimulus,sep="_")
#data$Filename <- paste(data$Filename,".txt",sep="")

emo_unblind <- right_join(goemo,data,by="Filename")
emo_unblind$Case <- substr(emo_unblind$Filename,1,1)
data2 <- emo_unblind

# Define emotions
#emo_unblind <- emo_unblind %>% group_by(participantID.x) %>% summarise_all(funs(mean))
emo_unblind$positive <- (emo_unblind$admiration + emo_unblind$amusement + emo_unblind$approval+
                           emo_unblind$caring + emo_unblind$desire + emo_unblind$excitement + emo_unblind$gratitude + emo_unblind$joy +
                           emo_unblind$love + emo_unblind$optimism + emo_unblind$pride + emo_unblind$relief)/12

emo_unblind$negative <- (emo_unblind$anger + emo_unblind$annoyance + emo_unblind$disappointment +         
                           emo_unblind$disapproval+emo_unblind$disgust+emo_unblind$embarrassment+
                           emo_unblind$fear+emo_unblind$grief+emo_unblind$nervousness +
                           emo_unblind$remorse+emo_unblind$sadness)/11

emo_unblind2 <- emo_unblind[,c("positive","negative")]
data_raw <- emo_unblind %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))
emo_unblind <- emo_unblind[ , -which(names(emo_unblind) %in% c("positive","negative","neutral"))]
emo_unblind2 <- normalize.rows(as.matrix(emo_unblind2),method="manhattan")
emo_unblind_norm <- cbind(emo_unblind,emo_unblind2)
emo_unblind_norm[,"pos_max"] <- apply(emo_unblind_norm[,c("admiration", "amusement","approval",
                           "caring", "desire", "excitement", "gratitude", 
                           "joy", "love","optimism", "pride", "relief")],1,max)
emo_unblind_norm[,"neg_max"] <- apply(emo_unblind_norm[,c("anger", "annoyance", "disappointment", "disapproval","disgust","embarrassment","fear","grief","nervousness", "remorse","sadness")],1,max)
data5 <- emo_unblind_norm %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))
data5$Case <- as.factor(substr(data5$id,1,1))

setwd("C:/Users/jakep/Dropbox/jakeLIWCanalyes")
library(xlsx)
library(irr)
stimuliRatings <- read.xlsx("evocativeVideoTask_stimuliRatings_2020-10-21.xlsx", sheetIndex = 1)
mydata <- select(stimuliRatings, contains("valence"))
mydata[mydata == ""] <- NA
mydata <- mydata[-c(1,2),]
mydata <- mydata[1:23,]
mydata <- mydata %>% select(matches("baby|dog|grandpa|phone|heart|bugear|lightsout|nuts|dying|coffe|larva|broken"))
```

## R Markdown

Key figures for the paper

TABLE: Demographics & clinical information for SZ and HC
Age
Education years
Symptom scores
PANSS+
CAINS
CPZ equivalents
any other relevant baseline measures
FIG: Group differences in trace (SZ vs HC)?
FIG: Prediction of group status by positive emotion alignment (AUC)
FIG: Oxytocin effects on trace in SZ?
FIG: Moderation of oxytocin effects in SZ by ... symptom severity, CPZ equivalents, attachment style

```{r table}
setwd("C:/Users/jakep/Desktop")
sz <- read.csv("PORQ_demographicAndBaselineDayData_labeled.csv")
#View(sz)
#sz <- load("PORQ_demographicAndBaselineDayData.r")
#sz$Item.1..Motivation.for.Close.Family.Spouse.Partner.Relationships <-
 # sub('^[^_]*_(\\d+).*', '\\1',sz$Item.1..Motivation.for.Close.Family.Spouse.Partner.Relationships)
 # as.numeric(gsub("([0-9]+).*$", "\\1", sz$Item.1..Motivation.for.Close.Family.Spouse.Partner.Relationships))
#  gsub("[^0-9.]", "",  sz$Item.1..Motivation.for.Close.Family.Spouse.Partner.Relationships)
for(i in 62:221){
  sz[,i] <- as.numeric(gsub("[^0-9.]", "",sz[,i]))
}
sz[,c("X")] <- as.numeric(gsub("[^0-9.]", "",sz[,"X"]))
sz$CPZ <- sz$X

# CAINS (NEGATIVE SYMPTOMS)
sz$CAINS <- sz[,62]+sz[,63]+sz[,64]+sz[,65]+sz[,66]+sz[,67]+sz[,68]+
  sz[,69]+sz[,70]+sz[,71]+sz[,72]+sz[,73]+sz[,74]
# neg symp with dose
#ggplot(data=sz, aes(x=CAINS, y=X))+geom_point()+geom_smooth(method=lm)
#cor(sz$CAINS, sz$X, use="complete.obs")
# PANSS
sz$PANSSpos <- sz[,75]+ sz[,76]+sz[,77]+sz[,78]+sz[,79]
sz$PANSSneg <- sz[,80]
sz$PANSSdisorganization <- sz[,81]+ sz[,82]+sz[,83]

# QLS
sz$QLS <- sz$Subscale.total.

# Role functioning scale
sz$RFS <- sz[,88]+sz[,89]+sz[,90]+sz[,91]

# Hinting Task
sz$Hinting <- sz$Total+sz$Total.1+sz$Total.2+sz$Total.3+sz$Total.4+
  sz$Total.5+sz$Total.6+sz$Total.7+sz$Total.8+sz$Total.9

# AMNART
sz$AMNART <- sz$Total.score

# Defeatest Beliefs
sz$Defeatist <- sz[,172]+sz[,173]+sz[,174]+sz[,175]+sz[,176]+sz[,178]+
  sz[,179]+sz[,180]+sz[,181]+sz[,182]+sz[,183]+sz[,184]+sz[,185]

# ECRRS
sz$ECRRS_Mom <- ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R.)+
  (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R.) +
  (8-sz$I.talk.things.over.with.this.person..R.) +
  (8-sz$I.find.it.easy.to.depend.on.this.person..R.)+
  sz$I.don.t.feel.comfortable.opening.up.to.this.person +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down. +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me +
  sz$I.m.afraid.that.this.person.may.abandon.me +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her)/9
sz$ECRRS_Mom_Attachment <- ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R.)+
  (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R.) +
  (8-sz$I.talk.things.over.with.this.person..R.) +
  (8-sz$I.find.it.easy.to.depend.on.this.person..R.))/4
sz$ECRRS_Mom_Avoidance <-
  (sz$I.don.t.feel.comfortable.opening.up.to.this.person +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down. +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me +
  sz$I.m.afraid.that.this.person.may.abandon.me +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her)/5
sz$ECRRS_Dad <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..1)+
  (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..1) +
  (8-sz$I.talk.things.over.with.this.person..R..1) +
  (8-sz$I.find.it.easy.to.depend.on.this.person..R..1)+
  sz$I.don.t.feel.comfortable.opening.up.to.this.person.1 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..1 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.1 +
  sz$I.m.afraid.that.this.person.may.abandon.me.1 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.1)/9
sz$ECRRS_Dad_Attachment <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..1)+
     (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..1) +
     (8-sz$I.talk.things.over.with.this.person..R..1) +
     (8-sz$I.find.it.easy.to.depend.on.this.person..R..1))/4
sz$ECRRS_Dad_Avoidance <- 
  (sz$I.don.t.feel.comfortable.opening.up.to.this.person.1 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..1 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.1 +
  sz$I.m.afraid.that.this.person.may.abandon.me.1 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.1)/5
sz$ECRRS_Friend <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..2)+
  (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..2) +
  (8-sz$I.talk.things.over.with.this.person..R..2) +
  (8-sz$I.find.it.easy.to.depend.on.this.person..R..2)+
  sz$I.don.t.feel.comfortable.opening.up.to.this.person.2 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..2 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.2 +
  sz$I.m.afraid.that.this.person.may.abandon.me.2 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.2)/9
sz$ECRRS_Friend_Attachment <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..2)+
     (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..2) +
     (8-sz$I.talk.things.over.with.this.person..R..2) +
     (8-sz$I.find.it.easy.to.depend.on.this.person..R..2))/4
sz$ECRRS_Friend_Avoidance <-   
  (sz$I.don.t.feel.comfortable.opening.up.to.this.person.2 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..2 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.2 +
  sz$I.m.afraid.that.this.person.may.abandon.me.2 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.2)/5
sz$ECRRS_Romantic <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..3)+
  (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..3) +
  (8-sz$I.talk.things.over.with.this.person..R..3) +
  (8-sz$I.find.it.easy.to.depend.on.this.person..R..3)+
  sz$I.don.t.feel.comfortable.opening.up.to.this.person.3 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..3 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.3 +
  sz$I.m.afraid.that.this.person.may.abandon.me.3 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.3)/9
sz$ECRRS_Romantic_Attachment <- 
  ((8-sz$It.helps.to.turn.to.this.person.in.times.of.need..R..3)+
      (8-sz$I.usually.discuss.my.problems.and.concerns.with.this.person..R..3) +
         (8-sz$I.talk.things.over.with.this.person..R..3) +
            (8-sz$I.find.it.easy.to.depend.on.this.person..R..3))/4
sz$ECRRS_Romantic_Avoidance <- 
  (sz$I.don.t.feel.comfortable.opening.up.to.this.person.3 +
  sz$I.prefer.not.to.show.this.person.how.I.feel.deep.down..3 +
  sz$I.often.worry.that.this.person.doesn.t.really.care.for.me.3 +
  sz$I.m.afraid.that.this.person.may.abandon.me.3 +
  sz$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.3)/5

sz$ECRRS <- apply(sz[,c("ECRRS_Mom", "ECRRS_Dad", "ECRRS_Friend",
                                   "ECRRS_Romantic")],1,mean, na.rm=TRUE)
sz$ECRRS_Attachment <- apply(sz[,c("ECRRS_Mom_Attachment", "ECRRS_Dad_Attachment", "ECRRS_Friend_Attachment",
            "ECRRS_Romantic_Attachment")],1,mean, na.rm=TRUE)
sz$ECRRS_Avoidance <- apply(sz[,c("ECRRS_Mom_Avoidance", "ECRRS_Dad_Avoidance", "ECRRS_Friend_Avoidance",
                                   "ECRRS_Romantic_Avoidance")],1,mean, na.rm=TRUE)

sz$id <- sz[,1]
sz$Case <- substr(sz$id,1,1)

#setwd("C:/Users/jakep/Dropbox/jakeLIWCanalyes")
#write.csv(sz, "PORQ_demographicAndBaselineDayData_labeled_scales_updated.csv")

table <- sz[,222:248]
table <- table %>% group_by(Case) %>% summarise_all(funs(mean(., na.rm = TRUE)))
sz2 <- sz %>% select(one_of(c('Case','Age','Years.of.Education','CPZ','CAINS','PANSSpos','QLS','RFS','AMNART','Hinting',
                              'Defeatist','ECRRS_Attachment','ECRRS_Avoidance')))
sz2[,c("Years.of.Education")] <- as.numeric(gsub("[^0-9.]", "",sz2[,c("Years.of.Education")]))
sz2 <- sz2 %>% group_by(Case)%>% summarise_all(funs(mean(., na.rm = TRUE)))
#write.csv(sz2, "Demographic_Table_For_Paper.csv")
print(sz2)
```

## Pos Align Plots

```{r pos}
data_joy <- data5 %>% filter(emo == "joy")
levels(data_joy$Case) <- list(Schizophrenia = "7",Healthy = "8")
t <- t.test(positive~Case, data=data_joy)
print(t)
ggplot(data_joy, aes(x=Case, y=positive))+geom_boxplot()+ggtitle("Positive Alignment Group Differences")
```

## Trace Plots


```{r pressure, echo=FALSE}
data6 <- data5 %>% filter(emo == "joy")
data6_r <- data6[,c("positive","negative")]
data6_r <- normalize.rows(as.matrix(data6_r),method="manhattan")
data6 <- data6[ , -which(names(data6) %in% c("positive","negative"))]
data6_r <- as.data.frame(data6_r)
data6_r2 <- cbind(data6,data6_r)
data7 <- data5 %>% filter(emo=="neg")
data7_r <- data7[,c("positive","negative")]
data7_r <- normalize.rows(as.matrix(data7_r),method="manhattan")
data7 <- data7[ , -which(names(data7) %in% c("positive","negative"))]
data7_r <- as.data.frame(data7_r)
data7_r2 <- cbind(data7,data7_r)
data67 <- inner_join(data6_r2, data7_r2, by="id")
data8 <- data5 %>% filter(emo == "neu")
data678 <- inner_join(data67, data8, by="id")
data678$trace <- data678$positive.x + data678$negative.y 
t3 <- t.test(trace~Case, data=data678)
print(t3)
levels(data678$Case) <- list(Schizophrenia = "7",Healthy = "8")
ggplot(data678,aes(x=Case,y=trace))+geom_boxplot()+ggtitle("Group Differences in Trace")
```

## Oxy v Pl

## ROC

```{r roc}
pred <- prediction( data678$trace, data678$Case )
perf <- performance( pred, "tpr", "fpr" )
text = performance(pred, "auc")@y.values
plot( perf, col="red")
text(.9,0.35,labels=paste("Trace_AUC =",text,sep=" "), cex=0.75)


pred <- prediction( data_joy$positive, data_joy$Case )
perf <- performance( pred, "tpr", "fpr" )
text = performance(pred, "auc")@y.values
plot( perf, col="blue", add=TRUE)
text(.9,0.3,labels=paste("PositiveAlignment_AUC =",text,sep=" "), cex=0.75)
```

```{r oxy}
# library(xlsx)
# library(dplyr)
# library(ggplot2)
# library(wordspace)
# setwd("C:/Users/jakep/Desktop")
# baseline_scales <- read.csv("PORQ_demographicAndBaselineDayData_labeled_scales.csv")
# Join on ID Day
data <- full_join(unblinding, evoc_trans, by="IDDay")
# replace na's for 8 with pl
data[is.na(data$drugCondition),c("drugCondition")] <- "PL"
# filter for only placebo
data$Case <- substr(data$participantID.y,1,1)
data <- data %>% filter(Case == "7")
# join to go emotions
setwd("C:/Users/jakep/Desktop")
goemo <- read.csv("go_emotions_output.csv")
goemo$Filename <- substr(goemo$file, 17,50) # get filename
goemo$id <- sapply(strsplit(goemo$Filename, "_"), "[", 1)
goemo$emo <- sapply(strsplit(goemo$Filename, "_"), "[", 2)
goemo$thing <- sapply(strsplit(goemo$Filename, "_"), "[", 3)
goemo <- goemo[-which(goemo$thing=="heart"),]
goemo$feeldescribe <- sapply(strsplit(goemo$Filename, "_"), "[", 4)
goemo <- goemo[grep("feel",goemo$feeldescribe),]
goemo$Filename <- paste(goemo$id,goemo$emo,goemo$thing, sep="_")
# Create variable for joining
data$Filename <- paste(data$participantID.y,data$stimulus,sep="_")
#data$Filename <- paste(data$Filename,".txt",sep="")

emo_unblind <- right_join(goemo,data,by="Filename")
emo_unblind$Case <- substr(emo_unblind$Filename,1,1)
data2 <- emo_unblind

# Define emotions
#emo_unblind <- emo_unblind %>% group_by(participantID.x) %>% summarise_all(funs(mean))
emo_unblind$positive <- (emo_unblind$admiration + emo_unblind$amusement + emo_unblind$approval+
                           emo_unblind$caring + emo_unblind$desire + emo_unblind$excitement + emo_unblind$gratitude + emo_unblind$joy +
                           emo_unblind$love + emo_unblind$optimism + emo_unblind$pride + emo_unblind$relief)/12

emo_unblind$negative <- (emo_unblind$anger + emo_unblind$annoyance + emo_unblind$disappointment +         
                           emo_unblind$disapproval+emo_unblind$disgust+emo_unblind$embarrassment+
                           emo_unblind$fear+emo_unblind$grief+emo_unblind$nervousness +
                           emo_unblind$remorse+emo_unblind$sadness)/11

emo_unblind2 <- emo_unblind[,c("positive","negative")]
data_raw <- emo_unblind %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))
emo_unblind <- emo_unblind[ , -which(names(emo_unblind) %in% c("positive","negative","neutral"))]
emo_unblind2 <- normalize.rows(as.matrix(emo_unblind2),method="manhattan")
emo_unblind_norm <- cbind(emo_unblind,emo_unblind2)
emo_unblind_norm[,"pos_max"] <- apply(emo_unblind_norm[,c("admiration", "amusement","approval",
                           "caring", "desire", "excitement", "gratitude", 
                           "joy", "love","optimism", "pride", "relief")],1,max)
emo_unblind_norm[,"neg_max"] <- apply(emo_unblind_norm[,c("anger", "annoyance", "disappointment", "disapproval","disgust","embarrassment","fear","grief","nervousness", "remorse","sadness")],1,max)
data5 <- emo_unblind_norm %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))

#data4 <- emo_unblind %>% filter(Case == "7")
# (1) average probability across all 1-positive, 2-negative and 3-neutral emotions
emo_unblind2 <- emo_unblind_norm %>% filter(drugCondition == "OT")
data5 <- emo_unblind2 %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))
data5$Case <- as.factor(substr(data5$id,1,1))
data6 <- data5 %>% filter(emo == "joy")
data7 <- data5 %>% filter(emo=="neg")
data67 <- inner_join(data6, data7, by="id")
data8 <- data5 %>% filter(emo == "neu")
data678 <- inner_join(data67, data8, by="id")
data678$trace <- data678$positive.x + data678$negative.y 
data678$Case <- substr(data678$id,1,1)

emo_unblind3 <- emo_unblind_norm %>% filter(drugCondition == "PL")
data5 <- emo_unblind3 %>% group_by(id, emo) %>% summarise_all(funs(mean(., na.rm = TRUE)))
data6 <- data5 %>% filter(emo == "joy")
data7 <- data5 %>% filter(emo=="neg")
data67 <- inner_join(data6, data7, by="id")
data8 <- data5 %>% filter(emo == "neu")
data789 <- inner_join(data67, data8, by="id")
data789$trace <- data789$positive.x + data789$negative.y
data789$Case <- substr(data789$id,1,1)


data678$drugCondition <- "OT"
data789$drugCondition <- "PL"
data789$Case.x <- as.factor(data789$Case.x)
data789$Case.y <- as.factor(data789$Case.y)
datarbind <- rbind(data678,data789)

#datanew <- inner_join(data678,data789, by="ID")

#t.test(datanew$trace.x,datanew$trace.y,paired=TRUE)
ggplot(datarbind, aes(y=trace,x=drugCondition))+geom_boxplot()+ggtitle("Trace Oxytocin Placebo Differences")
```
