---
title: "2020_09_05_Accuracy_Scale_Figures"
author: "Jake Portanova"
date: "September 5, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(xlsx)
setwd("C:/Users/jakep/Desktop")
baseline_scales <- read.csv("PORQ_demographicAndBaselineDayData_labeled_scales.csv")
ratings <- read.csv("PORQ_animatedShapes_ratings.csv")
ratings$composite <- ratings$accuracy_rater1 +ratings$accuracy_rater2+ratings$intentionality_rater1+
  ratings$intentionality_rater2
ratings$intentionality <- ratings$intentionality_rater1 + ratings$intentionality_rater2
ratings$accuracy <- ratings$accuracy_rater1 + ratings$accuracy_rater2
ratings$ID <- as.character(ratings[,1])
baseline_scales$ID <- as.character(baseline_scales[,2])
ratings_scales <- inner_join(ratings, baseline_scales, by="ID")
ratings_scales$Case <- as.factor(substr(ratings_scales$ID,1,1))
ratings_scales$condition <- gsub("[0-9.+]", "", ratings_scales$stimulus)
# Unblind Data
setwd("C:/Users/jakep/Dropbox/PORQ_dataForUW")
drugunblind <- read.xlsx("PORQ_drugUnblinding.xlsx", sheetIndex =1)
# Make all 3 on the same graph
```

### PCA
```{r}
mydata <- baseline_scales[,63:75]
mydata <- na.omit(mydata)
fit <- princomp(mydata, cor=TRUE)
summary(fit) # print variance accounted for
loadings(fit) # pc loadings
plot(fit,type="lines") # scree plot
fit$scores # the principal components
biplot(fit)

# AMNART
mydata <- baseline_scales[,187:222]
mydata2 <- baseline_scales[,c(2,214:222)]
mydata2$ECRRS_romantic <- mydata2$It.helps.to.turn.to.this.person.in.times.of.need..R..3+
  mydata2$I.usually.discuss.my.problems.and.concerns.with.this.person..R..3 +
  mydata2$I.talk.things.over.with.this.person..R..3 +
  mydata2$I.find.it.easy.to.depend.on.this.person..R..3+
(8- mydata2$I.don.t.feel.comfortable.opening.up.to.this.person.3) +
  (8-mydata2$I.prefer.not.to.show.this.person.how.I.feel.deep.down..3) +
  (8-mydata2$I.often.worry.that.this.person.doesn.t.really.care.for.me.3) +
  (8-mydata2$I.m.afraid.that.this.person.may.abandon.me.3) +
  (8-mydata2$I.worry.that.this.person.won.t.care.about.me.as.much.as.I.care.about.him.or.her.3)
# mydata2$ID <- mydata2[,1]
# ggplot(mydata2, aes(x=Anxiety,y=Attachment))+geom_point()+
#   ggrepel::geom_text_repel(aes(label = ID), color = "black", size = 2.5, segment.color = "grey")
mydata <- na.omit(mydata2)
fit <- princomp(mydata, cor=TRUE)
summary(fit) # print variance accounted for
loadings(fit) # pc loadings
plot(fit,type="lines") # scree plot
fit$scores # the principal components
biplot(fit, cex=.3)
PCbiplot <- function(PC, x="PC1", y="PC2") {
    # PC being a prcomp object
    data <- data.frame(obsnames=row.names(PC$x), PC$x)
    plot <- ggplot(data, aes_string(x=x, y=y)) + geom_text(alpha=.4, size=3, aes(label=obsnames))
    plot <- plot + geom_hline(aes(0), size=.2) + geom_vline(aes(0), size=.2)
    datapc <- data.frame(varnames=rownames(PC$rotation), PC$rotation)
    mult <- min(
        (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
        (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
        )
    datapc <- transform(datapc,
            v1 = .7 * mult * (get(x)),
            v2 = .7 * mult * (get(y))
            )
    plot <- plot + coord_equal() + geom_text(data=datapc, aes(x=v1, y=v2, label=varnames), size = 5, vjust=1, color="red")
    plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2), arrow=arrow(length=unit(0.2,"cm")), alpha=0.75, color="red")
    plot
}
PC <- prcomp(mydata)
PCbiplot(fit2,x="PC1",y="PC2")
```
### Accuracy V Condition
```{r condition v accuracy, echo=FALSE, warning=FALSE}
ggplot(ratings_scales, aes(x=condition, y=accuracy, color=Case))+geom_boxplot()+geom_smooth(method=lm)
ratings_scales %>% group_by(Case, condition)%>% summarise(acc = mean(accuracy, na.rm=TRUE),int=mean(intentionality, na.rm=TRUE))+ggtitle("Accuracy by Condition")                              
```
### Hinting v accurary and intentionality

```{r hinting}
cor(ratings_scales$Hinting, ratings_scales$accuracy, use="complete.obs")
cor(ratings_scales$Hinting, ratings_scales$intentionality, use="complete.obs")
```

### MEDS V POSITIVE AND NEGATIVE SYMPTOMS + Age
```{r meds,echo=FALSE,warning=FALSE}
cor(ratings_scales$CAINS,ratings_scales$X, use="complete.obs")
ggplot(ratings_scales, aes(x=X,y=CAINS))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=PANSSpos, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=PANSSneg, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=PANSSdisorganization, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=RFS, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=QLS, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=Defeatist, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=Hinting, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=ECRRS, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=ECRRSmom, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=ECRRSdad, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=ECRRSromantic, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X,y=ECRRSfriend, size=Age))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=Age,y=X))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=Age,y=CAINS))+geom_point()+geom_smooth(method=lm)
```


## Delusions v accuracy/intentionality
```{r delusions, echo=FALSE, warning=FALSE}
ratings_scales2 <- ratings_scales %>% filter(condition == "tom")
ggplot(ratings_scales, aes(x=X2..Delusions, y=accuracy))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales2, aes(x=X2..Delusions, y=accuracy))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales, aes(x=X2..Delusions, y=intentionality))+geom_point()+geom_smooth(method=lm)
ggplot(ratings_scales2, aes(x=X2..Delusions, y=intentionality))+geom_point()+geom_smooth(method=lm)
```

## Accuracy versus Scales

Here are some plots with the scales and accuracy. The error bar is the standard error. The standard error of the regression provides the absolute measure of the typical distance that the data points fall from the regression line.

```{r accuracy, warning=FALSE}
# QLS
ggplot(ratings_scales, aes(x=QLS , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)
# RFS
ggplot(ratings_scales, aes(x=RFS , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# CAINS
ggplot(ratings_scales, aes(x=CAINS , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS NEG
ggplot(ratings_scales, aes(x=PANSSneg , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS POS
ggplot(ratings_scales, aes(x=PANSSpos , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS POS
ggplot(ratings_scales2, aes(x=PANSSpos , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS disorganization
ggplot(ratings_scales, aes(x=PANSSdisorganization , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# AMNART
ggplot(ratings_scales, aes(x=AMNART , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# Hinting
ggplot(ratings_scales, aes(x=Hinting , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# Defeatist
ggplot(ratings_scales, aes(x=Defeatist , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)

# ECRRS
ggplot(ratings_scales, aes(x=ECRRS , y=accuracy, color=Case))+geom_point()+geom_smooth(method=lm)
```

## intentionality versus Scales

Here are some plots with the scales and intentionality

```{r intentionality, warning=FALSE}
# QLS
ggplot(ratings_scales, aes(x=QLS , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)
# RFS
ggplot(ratings_scales, aes(x=RFS , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# CAINS
ggplot(ratings_scales, aes(x=CAINS , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS NEG
ggplot(ratings_scales, aes(x=PANSSneg , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS POS
ggplot(ratings_scales, aes(x=PANSSpos , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS disorganization
ggplot(ratings_scales, aes(x=PANSSdisorganization , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# AMNART
ggplot(ratings_scales, aes(x=AMNART , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# Hinting
ggplot(ratings_scales, aes(x=Hinting , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# Defeatist
ggplot(ratings_scales, aes(x=Defeatist , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)

# ECRRS
ggplot(ratings_scales, aes(x=ECRRS , y=intentionality, color=Case))+geom_point()+geom_smooth(method=lm)
```

## composite versus Scales

Here are some plots with the scales and composite

```{r composite, warning=FALSE}
# QLS
ggplot(ratings_scales, aes(x=QLS , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)
# RFS
ggplot(ratings_scales, aes(x=RFS , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# CAINS
ggplot(ratings_scales, aes(x=CAINS , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS NEG
ggplot(ratings_scales, aes(x=PANSSneg , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS POS
ggplot(ratings_scales, aes(x=PANSSpos , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# PANSS disorganization
ggplot(ratings_scales, aes(x=PANSSdisorganization , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# AMNART
ggplot(ratings_scales, aes(x=AMNART , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# Hinting
ggplot(ratings_scales, aes(x=Hinting , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# Defeatist
ggplot(ratings_scales, aes(x=Defeatist , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)

# ECRRS
ggplot(ratings_scales, aes(x=ECRRS , y=composite, color=Case))+geom_point()+geom_smooth(method=lm)
```
